Optimal updating factor in adaptive flat-distribution-sampling simulations

### 2016-04-21 doc/invt.tex
invt.tex: small edits

In the above, we have focused on
the asymptotic error.
%
For a finite-length simulation,
we should include the residual part
and minimize the total error.
%
For the bandpass updating schemes,
this leads to the optimal value
of the free parameter, $t_0$,
which is, according to Eq. \eqref{eq:half_alpha0}
%
%%Assuming the system is initially equilibrated
%%under a constant updating magnitude,
%%$\alpha_0$,
%Assuming Eq. \eqref{eq:error_res1} with
%$$
%q(T)
%=
%\int_0^T \frac{ dt } { t + t_0 }
%=
%\ln \frac{ T + t_0 } { t_0 }.
%$$
%%
%we have, from Eqs. \eqref{eq:error_split}
%and \eqref{eq:error_asym_sinc},
%%
%\begin{equation}
%  E
%  =
%  E_R + E_A
%  =
%  \frac { \frac 1 2 \alpha_0 \, t_0^2 + T }
%        {          ( T + t_0 )^2          }
%  \sum_{ k = 2 }^K \Gamma_k
%  .
%\notag
%%\label{eq:error_sinc0}
%\end{equation}
%%
%The minimum is reached at
%
\begin{equation}
  t_0
  =
  \frac{     2    }
       { \alpha_0 }
  ,
\label{eq:t0_sinc}
\end{equation}
%
and at this point
%
\begin{equation}
  E
  =
  \frac{   1     }
       { T + t_0 }
  \sum_{ k = 2 }^K
    \Gamma_k
  .
\label{eq:error_sinc}
\end{equation}
%
In Appendix \ref{sec:equilerr},
we show that the above error tends
to the error of the ideal equilibrium FDS simulation
in the asymptotic limit.

@@

Initially,
we set the bias potential to zero,
$V_i \equiv 0$,
%
and equilibrate the system under
a constant updating magnitude,
$\alpha_0 = 10^{-4}$.
%
After this,
we reset the origin of the time, $t$,
and started the testing schedule.
%specified by either
%Eq. \eqref{eq:q_opt}
%or
%Eq. \eqref{eq:alpha_invtlambda}.

@@

For the single-bin updating scheme,
we chose $\alpha_0 = 10^{-4}$
and ran the simulation for $T = 10^8$ steps.
%
As shown in Fig. \ref{fig:errsbin},
the numerical results of the terminal error agreed well with
the analytical prediction by Eq. \eqref{eq:error_invt}.
%
For both global and local sampling processes,
the optimal $\lambda$ occurred around $1.0$,
verifying the optimality of Eq. \eqref{eq:alpha_invt1}.
%
%Recall that $1/\lambda$ in Eq. \eqref{eq:alpha_invtlambda}
%represents the relative updating magnitude.
%%
%Figure \ref{fig:errsbin} also shows
%an asymmetry of the error curve.
%A smaller than optimal value of
%the updating magnitude, $1/\lambda$,
%tends to increase the error more rapidly
%than a larger than optimal value,
%suggesting that the over-updating
%is generally preferable to the under-updating
%when the optimal value is unknown.
%
The two error functions
differed only by a multiplicative constant,
which again agreed with the theory:
%
with identical eigenvalues,
$\lambda_2 = \cdots = \lambda_n = 1$,
the error in Eq. \eqref{eq:error_invt}
depends on the sampling process only through
the sum $\sum_{ k = 2 }^n \Gamma_k$,
which gives rise to the above multiplicative constant.

@@

As an example of the multiple-bin schemes,
we chose the nearest-neighbor updating scheme
described in Sec. \ref{sec:nnscheme}.
%
We choose $\mu_1 = 0.24$ to the smallest eigenvalue
close to zero.
%
Again, simulation and theory agreed well,
as shown in Fig. \ref{fig:errnnbr}.
%
The normalized error
and the optimal value of $1/\lambda$,
depended on the simulation length, $T$,
in the global sampling case,
because of the near-zero eigenvalues,
as discussed in Appendix \ref{sec:invt_schedule}.
%
%The optimal $1/\lambda$ gradually increased
%with simulation length,
%as discussed in Sec. \ref{sec:optlambda}.
%
However, for the local sampling case,
the $T$-dependence was suppressed
because of the dominance of large $\Gamma_k$'s
of the small-$k$ modes.
%
The optimal $\lambda$ remained around $1.0$,
as suggested by Eq. \eqref{eq:lambda_nn_onestep}.

@@

In conclusion,
we have proposed a method of computing
the optimal schedule of the updating magnitude
for a general adaptive FDS simulation,
e.g., the WL algorithm or metadynamics.
%
Adaptive FDS methods
effectively sample a flat distribution
by incrementally updating the bias potential
to offset the PMF.
%
The optimal schedule ensures fastest convergence
of the bias potential.
%They differ by the updating schemes,
%which specify how the bias potential is modified
%in each updating step.
%%
%In the single-bin or WL case,
%the update is limited to the current bin;
%while in the metadynamics case,
%the bias potential of a neighborhood of the current one
%is updated with relative weight specified by a Gaussian window.

Each adaptive FDS method is associated with
an updating scheme,
or mathematically an updating matrix,
whose elements $w_{ij}$ specifies the
relative magnitude of updating the bias potential
at bin $i$ upon a visit to bin $j$.
%
Our method computes the optimal schedule from
the eigenvalues of the updating matrix,
and the integrals of the autocorrelation functions
of the eigenmodes.
%
For the single-bin (WL) scheme,
the optimal schedule from our method
is given by inverse-time formula,
Eq. \eqref{eq:alpha_invt1}.
%
The parameter, $t_0$, can be adjusted
according to Eq. \eqref{eq:t0_sinc},
to accommodate the initial error.
%such that the initial updating magnitude
%is half of the previous equilibrium value.
%
For a general multiple-bin scheme,
including the Gaussian one used in metadynamics,
the optimal schedule has no closed form,
but is given by an equation of motion
of a free particle with a position-dependent mass, Eq. \eqref{eq:q_opt}.
%
In this case,
the optimal schedule and error
can be sensitive to the simulation length.

We have also shown that
the single-bin scheme is optimal
in the long time limit
without a priori assumption
on the smoothness of the PMF.
%
More generally, with perfect filtering
of certain eigenmodes, we can construct a
class of multiple-bin bandpass updating schemes
that are also optimal for asymptotic convergence.
%
The optimal schedule of these bandpass schemes
is always given by the inverse-time formula.
%
They appeared to outperform similar Gaussian schemes
in our model study,
suggesting that they can be useful
in high-precision metadynamics simulations.

Strictly speaking, our theory is valid
only for long simulations.
%
This allows us to assume the sampling process
to be a quasi-equilibrium one,
and to represent the autocorrelation function
of each eigenmode by a single number, $\Gamma_k$.
%
Although these assumptions appeared to work well
on the model system,
they may break down for relatively short simulations
of glassy systems.

@@

Here we give a program of computing
the optimal schedule and the error
of a given adaptive FDS simulation.
%
Basically, we extract
both $\lambda_i$'s and $\Gamma_i$'s
from the input,
and then feed them to Eq. \eqref{eq:q_opt}
for the schedule.
%
The dependence of variables are shown in Fig. \ref{fig:vardep}.

@@

  \node[draw, text width={width("Optimal")}]
    (qT) at (4.7, 1) {Optimal\\ $q(T)$};

@@

  %\node[inner sep=0, minimum size=0] (R1) at (3.6, 1) {};
  %\node[inner sep=0, minimum size=0] (R2) at (4.6, 0) {};
  %\node[inner sep=0, minimum size=0] (R3) at (5.7, 1) {};

@@

  \draw[->, >=latex, thick]
    (lambda) -| (M1)
    (gamma)  -- (M1)
    (T)      -| (M1)
    (M1)     -- (qT);

  \draw[->, >=latex, thick]
    (qT) -- (N1)
    (N1) |- (alpha);

@@

  \draw[->, >=latex, thick]
    (M1) edge[bend left=70] (N1);
    %(R1) |- (R2) -| (R3);
\end{tikzpicture}
\caption{
  \label{fig:vardep}
  Dependence of variables in computing
  the optimal schedule and the error.
}
\end{figure}

@@

Using Eq. \eqref{eq:alpha_invtlambda}
in Eq. \eqref{eq:error_asym1} yields
%
\begin{align}
\Err_A
&=
\frac{    1    }
     { T + t_0 }
\sum_{k = 2}^n
  \frac{ \Gamma_k \, \nu_k^2 }
       {    2 \, \nu_k - 1   }
\left[
  1 - \left(
        \frac {     t_0 }
              { T + t_0 }
      \right)^{ 2 \, \nu_k - 1 }
\right],
\label{eq:error_asym_invt}
\end{align}
%
where $\nu_k \equiv \lambda_k / \lambda$.
%
Assuming Eq. \eqref{eq:error_res1}
for the residual error, and Eq. \eqref{eq:t0_sinc},
we get
%
\begin{equation}
\Err_R
=
\sum_{k = 2}^n
  \frac{ \Gamma_k \, \nu_k }
       {        t_0   }
  \left(
      \frac{   t_0   }
           { T + t_0 }
   \right)^{ 2 \, \nu_k },
\notag
%\label{eq:error_res_invt}
\end{equation}
%
with
$
  q(T)
  =
  ( 1 / \lambda )
  \ln\left(
    1 + T / t_0
  \right)
$
%
from integrating Eq. \eqref{eq:alpha_invtlambda}.
%
%We assume that
%the system was initially equilibrated
%at a constant $\alpha_0$,
%such that the values of
%$\left\langle y_k^2(0) \right\rangle$
%can be computed from Eq. \eqref{eq:y2_eql},
%as well as Eq. \eqref{eq:t0_sinc}.
%
The total error is
%
\begin{align}
\Err
&=
\Err_R + \Err_A
\notag
\\
&=
\sum_{ k = 2 }^n
  \frac
  {
    \Gamma_k \, \nu_k \,
    \left[
      \nu_k
      +
      (\nu_k - 1)
      \left(
        \frac{ t_0 } { T + t_0 }
      \right)^{ 2 \, \nu_k - 1 }
    \right]
  }
  {
    (T + t_0) \, (2 \, \nu_k - 1)
  }
  .
\label{eq:error_invt}
\end{align}
%

\subsection{\label{sec:deplength}
Dependence on the simulation length}

The parameter, $\lambda$, is equal to
the difference
$$
  \lambda
  =
  \Delta \left( \frac{ 1 } { T \, \alpha } \right)
  \equiv
  \left.
  \frac { 1 } { T \, \alpha(t) }
  \right|_{t = 0}^{t = T}
  .
$$
which corresponds to the height difference
of the normalized mass distribution
$
\left. m(q) \right|_{q = 0}^{q = q(T)}
$
in the optimal schedule
(cf. Sec. \ref{sec:mass_distr}).
%
Therefore, we expect the optimal $\lambda$
to decrease with the span $q(T)$,
hence the simulation length $T$,
if the distribution has a long tail.

\subsection{Nearest-neighbor updating scheme}

For the nearest-neighbor updating scheme
introduced in Sec. \ref{sec:nnscheme},
we can find an analytical expression
of the optimal value of $\lambda$
in the large-$n$ limit.
%
In this case,
we
drop the second term in the square brackets
of Eq. \eqref{eq:error_asym_invt},
which vanishes asymptotically if $2 \, \nu_k > 1$,
and convert the asymptotic error
to an integral:
%$\sum_i \to \frac{2 \, n}{\pi} \int_0^{\pi/2} dp$, and
%
\begin{align}
\Err_A
=
\frac{2 \, n}{\pi \, T}
\int_0^{\pi/2}
  \frac{ \Gamma(p) \, \left(1 - 4 \, \mu_1 \, \sin^2 p \right)^2    }
       {   \lambda \, \left(2 - 8 \, \mu_1 \, \sin^2 p - \lambda \right) }
\, dp.
\notag
%\label{eq:error_nn_asym_int}
\end{align}

@@

>>>>

In the above, we have focused on
the asymptotic error.
%
For a finite-length simulation,
we should include the residual part
and minimize the total error.
%
For the bandpass updating schemes,
this leads to the optimal value
of the free parameter, $t_0$,
which is, according to Eq. \eqref{eq:half_alpha0},
%
%%Assuming the system is initially equilibrated
%%under a constant updating magnitude,
%%$\alpha_0$,
%Assuming Eq. \eqref{eq:error_res1} with
%$$
%q(T)
%=
%\int_0^T \frac{ dt } { t + t_0 }
%=
%\ln \frac{ T + t_0 } { t_0 }.
%$$
%%
%we have, from Eqs. \eqref{eq:error_split}
%and \eqref{eq:error_asym_sinc},
%%
%\begin{equation}
%  E
%  =
%  E_R + E_A
%  =
%  \frac { \frac 1 2 \alpha_0 \, t_0^2 + T }
%        {          ( T + t_0 )^2          }
%  \sum_{ k = 2 }^K \Gamma_k
%  .
%\notag
%%\label{eq:error_sinc0}
%\end{equation}
%%
%The minimum is reached at
%
\begin{equation}
  t_0
  =
  \frac{     2    }
       { \alpha_0 }
  ,
\label{eq:t0_sinc}
\end{equation}
%
and at this point
%
\begin{equation}
  E
  =
  \frac{   1     }
       { T + t_0 }
  \sum_{ k = 2 }^K
    \Gamma_k
  .
\label{eq:error_sinc}
\end{equation}
%
In Appendix \ref{sec:equilerr},
we show that the above error tends
to the error of the ideal equilibrium FDS simulation
in the asymptotic limit.

@@

Initially,
we set the bias potential to zero,
$V_i \equiv 0$,
%
and equilibrate the system for $10^7$ steps
under a constant updating magnitude,
$\alpha_0 = 10^{-4}$,
unless specified otherwise.
%
After this,
we reset the origin of the time, $t$,
and started the testing schedule.
%specified by either
%Eq. \eqref{eq:q_opt}
%or
%Eq. \eqref{eq:alpha_invtlambda}.

@@

For the single-bin updating scheme, we
%we chose $\alpha_0 = 10^{-4}$ and
ran the simulation for $T = 10^8$ steps.
%
As shown in Fig. \ref{fig:errsbin},
the numerical results of the terminal error agreed well with
the analytical prediction.
%
For both global and local sampling processes,
the optimal $\lambda$ occurred around $1.0$,
verifying the optimality of Eq. \eqref{eq:alpha_invt1}.
%
%Recall that $1/\lambda$ in Eq. \eqref{eq:alpha_invtlambda}
%represents the relative updating magnitude.
%%
%Figure \ref{fig:errsbin} also shows
%an asymmetry of the error curve.
%A smaller than optimal value of
%the updating magnitude, $1/\lambda$,
%tends to increase the error more rapidly
%than a larger than optimal value,
%suggesting that the over-updating
%is generally preferable to the under-updating
%when the optimal value is unknown.
%
The two error functions
differed only by a multiplicative constant,
also in agreement with the theory
(cf. Appendix \ref{sec:invt_singlebin}).
%

@@

As an example of the multiple-bin schemes,
we chose the nearest-neighbor updating scheme
described in Sec. \ref{sec:nnscheme}.
%
We chose $\mu_1 = 0.24$ to make the smallest eigenvalue
close to zero.
%
Again, simulation and theory agreed well,
as shown in Fig. \ref{fig:errnnbr}.
%
The optimal value of $1/\lambda$,
increased with the simulation length, $T$,
in the global sampling case
(cf. Appendix \ref{sec:invt_deplength}).
%
However, the shift was suppressed
for the local sampling case,
with the optimal $\lambda$ remained around $1.0$
[cf. Eq. \eqref{eq:lambda_nn_onestep}].

@@

In conclusion,
we have proposed a method of computing
the optimal schedule of the updating magnitude
for a general adaptive FDS simulation,
e.g., the WL algorithm or metadynamics.
%
Adaptive FDS methods
effectively sample a flat distribution
by incrementally updating the bias potential
to offset the PMF.
%
The optimal schedule delivers fastest convergence
of the bias potential.
%They differ by the updating schemes,
%which specify how the bias potential is modified
%in each updating step.
%%
%In the single-bin or WL case,
%the update is limited to the current bin;
%while in the metadynamics case,
%the bias potential of a neighborhood of the current one
%is updated with relative weight specified by a Gaussian window.

Each adaptive FDS method is associated with
an updating scheme,
or mathematically an updating matrix.
%whose elements $w_{ij}$ specifies the
%relative magnitude of updating the bias potential
%at bin $i$ upon a visit to bin $j$.
%
Our method computes the optimal schedule from
the eigenvalues of the updating matrix,
and the integrals of the autocorrelation functions
of the eigenmodes.
%
For the single-bin (WL) scheme,
the optimal schedule from our method
is given by the inverse-time formula,
Eq. \eqref{eq:alpha_invt1}.
%
For a general multiple-bin scheme,
including the Gaussian one used in metadynamics,
the optimal schedule has no closed form,
but is given by an equation of motion
of a free particle with a position-dependent mass, Eq. \eqref{eq:q_opt}.
%
In this case,
the optimal schedule and error
can be sensitive to the simulation length.
%
The initial updating magnitude is always
half of the previous equilibrium value.
% the value used during equilibration.

We have also shown that
the single-bin scheme is optimal
in the long time limit
without a priori assumption
on the smoothness of the PMF.
%
More generally, with perfect filtering
of certain eigenmodes, we can construct a
class of bandpass updating schemes
that are also optimal for asymptotic convergence.
%
The optimal schedule of these bandpass schemes
is always given by the inverse-time formula.
%
They appeared to outperform similar Gaussian schemes
in our model study,
and they can be useful
for high-precision metadynamics simulations.
%
However, since the bandpass schemes
update the bias potential globally,
they can be more expensive than
the Gaussian schemes.
%
Besides, the performance gain
is relative small for a shorter simulation
with a local sampling process such as MD.

Strictly speaking, our method is valid
only for long simulations.
%
This allows us to assume the sampling process
to be a quasi-equilibrium one,
and to represent the autocorrelation function
of each eigenmode by a single number, $\Gamma_k$.
%
Although these assumptions appeared to work well
on our test system,
they may break down for relatively short simulations
of glassy systems.

@@

Here we give a program of computing
the optimal schedule and the error
of a given adaptive FDS simulation.
%
Basically, we need to extract
$\lambda_i$'s and $\Gamma_i$'s
from the input,
and then feed them to Eq. \eqref{eq:q_opt}
for the schedule.
%
The dependence of variables are shown in Fig. \ref{fig:vardep}.

@@

  \node[draw, text width={width("Optimal")}]
    (qT) at (4.6, 1.4) {Optimal\\ $q(T)$};

@@

  \node[inner sep=0, minimum size=0] (R1) at (3.6, 1) {};
  \node[inner sep=0, minimum size=0] (R2) at (4.6, 0.6) {};
  \node[inner sep=0, minimum size=0] (R3) at (5.6, 1) {};

@@

  \draw[->, >=latex, thick]
    (lambda) -| (M1)
    (gamma)  -- (M1)
    (T)      -| (M1)
    (M1)     -- (R1)
    (R1)     |- (qT);

  \draw[->, >=latex, thick]
    (qT)     -| (R3);

  \draw[->, >=latex, thick]
    (R3) -- (N1) |- (alpha);

@@

  \draw[->, >=latex, thick]
    %(M1) edge[bend left=70] (N1);
    (R1) |- (R2) -| (R3);
\end{tikzpicture}
\caption{
  \label{fig:vardep}
  Dependence of variables in computing
  the optimal schedule and the error.
}
\end{figure}

@@

Using Eq. \eqref{eq:alpha_invtlambda}
in Eq. \eqref{eq:error_asym1} yields
%
\begin{align}
  \Err_A
  &=
  \frac{    1    }
       { T + t_0 }
  \sum_{k = 2}^n
    \frac{ \Gamma_k \, \nu_k^2 }
         {    2 \, \nu_k - 1   }
  \left[
    1 - \left(
          \frac {     t_0 }
                { T + t_0 }
        \right)^{ 2 \, \nu_k - 1 }
  \right]
  ,
\label{eq:error_asym_invt}
\end{align}
%
where $\nu_k \equiv \lambda_k / \lambda$.
%
From Eq. \eqref{eq:error_res1},
we get
%
\begin{equation}
  \Err_R
  =
  \frac { \alpha_0 } { 2 }
  \sum_{k = 2}^n
  \Gamma_k \, \lambda_k \,
  \left(
      \frac{   t_0   }
           { T + t_0 }
  \right)^{ 2 \, \nu_k }
  .
\label{eq:error_res_invt}
\end{equation}
%
The total error is the sum of the two.
%with
%$
%  q(T)
%  =
%  ( 1 / \lambda )
%  \ln\left(
%    1 + T / t_0
%  \right)
%$
%%
%from integrating Eq. \eqref{eq:alpha_invtlambda}.
%
%We assume that
%the system was initially equilibrated
%at a constant $\alpha_0$,
%such that the values of
%$\left\langle y_k^2(0) \right\rangle$
%can be computed from Eq. \eqref{eq:y2_eql},
%as well as Eq. \eqref{eq:t0_sinc}.
%
%The total error is
%%
%\begin{align}
%\Err
%&=
%\Err_R + \Err_A
%\notag
%\\
%&=
%\sum_{ k = 2 }^n
%  \frac
%  {
%    \Gamma_k \, \nu_k \,
%    \left[
%      \nu_k
%      +
%      (\nu_k - 1)
%      \left(
%        \frac{ t_0 } { T + t_0 }
%      \right)^{ 2 \, \nu_k - 1 }
%    \right]
%  }
%  {
%    (T + t_0) \, (2 \, \nu_k - 1)
%  }
%  .
%%\notag
%\label{eq:error_invt}
%\end{align}

\subsection{\label{sec:invt_singlebin}
  Single-bin updating scheme
}

For the single-bin scheme, we have
$\lambda_2 = \cdots = \lambda_n = 1$,
and
the errors
%from Eqs. \eqref{eq:error_res_invt}
%and \eqref{eq:error_asym_invt}
depend on $\Gamma_k$'s only via the sum
$\sum_{k = 2}^n \Gamma_k$,
which serves as a multiplicative constant.

In the asymptotic limit,
we can focus on the asymptotic error
and drop the second term in the square brackets
of Eq. \eqref{eq:error_asym_invt}
by assuming $\lambda < 2$.
%
Then,
$$
  E_A
  =
  \frac { 1 } { T + t_0 }
  \frac {             1            }
        { \lambda \, (2 - \lambda) }
  \sum_{ k = 2 }^n \Gamma_k
  ,
$$
is minimal at $\lambda = 1$.
%
\note{A higher-order correction:
  $
  \lambda = 1 -
  \left[
    1 - \frac 1 2 \alpha_0 \, (T+t_0)
  \right] r \, \log r
  ,
  $
  where $r = t_0 / (T + t_0)$.
}

\subsection{\label{eq:invt_nn}
Nearest-neighbor updating scheme}

For the nearest-neighbor updating scheme
introduced in Sec. \ref{sec:nnscheme},
we can find an analytical expression
of the optimal value of $\lambda$
in the large-$n$ and asymptotic limit.
%
In this case,
if $2 \, \nu_k > 1$ for every $k$,
the asymptotic error is given by the integral
%$\sum_i \to \frac{2 \, n}{\pi} \int_0^{\pi/2} dp$, and
%
\begin{align}
  \Err_A
  =
  \frac{ 2 \, n  }
       { \pi \, T }
  \int_0^{\pi/2}
    \frac{ \Gamma(p) \, \left(1 - 4 \, \mu_1 \, \sin^2 p \right)^2    }
         {   \lambda \, \left(2 - 8 \, \mu_1 \, \sin^2 p - \lambda \right) }
  \, dp
  .
\notag
%\label{eq:error_nn_asym_int}
\end{align}

@@

\subsection{\label{sec:invt_deplength}
Dependence on the simulation length}

For a finite-length simulation,
we generally expect the optimal $\lambda$
that minimizes the total error to
decrease with the simulation length $T$.
%
From Eq. \eqref{eq:alpha_invt}, we have
$$
  \lambda
  =
  \Delta \left( \frac{ 1 } { T \, \alpha } \right)
  \equiv
  \left.
  \frac { 1 } { T \, \alpha(t) }
  \right|_{t = 0}^{t = T}
  .
$$
This expression corresponds to the height difference
of the mass distribution
$
\bigl. m(Q) \bigr|_{Q = q(T)}^{Q = 0}
$
in the optimal schedule
(cf. Sec. \ref{sec:mass_distr}).
%
With a fixed $\alpha_0$,
increasing the simulation length $T$
also increases the optimal span $q(T)$ of the distribution
(cf. Sec. \ref{sec:optinitalpha}),
and thus reduces the height difference.
%
This effect is significant
if the distribution $m(Q)$ has a long tail,
or if some eigenvalues $\lambda_k$'s are near zero.
%
It is often suppressed in local sampling processes,
because the eigenmodes with large $\lambda_k$'s
are accompanied by large $\Gamma_k$'s,
which shortens the distribution tail.
